A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-03-25 leonid_rebuttal.txt

We thank the reviewers for detailed feedback!

We will take your comments into account to correct and improve the 
presentation.  We will also address concerns raised in the reviews 
as outlined below.

Reviewer A
~~~~~~~~~~

Relation to algorithms that compute the winning region:

Our technique can indeed be seen as a hybrid between 
counterexample-guided synthesis and traditional winning region 
computation.  By letting the former guide the exploration, we are 
able to solve the game while learning fewer states.  This is the 
aim of the abstraction refinement framework, to restrict the 
dueling solvers to consider only opponent moves that may lead
to spoiling strategies.  As the reviewer points out, this allows 
computing deeper stategies where other methods hit the state 
explosion barrier.

Deriving losing states from a specific Abstract Game Tree (AGT):

Assume that player $P$ loses from state $s$ when the opponent $O$ 
plays according to AGT $t$.  This means that there exists a 
winning opponent stategy from $s$, hence the state is losing for 
$P$ by definition and can be added to the set of losing states for 
the entire game.

Note that the opposite is not true: assuming that $P$ can win from 
$s$ when $O$ plays according to $t$, $s$ is not necessarily a 
winning state for $P$, as there may exist a different AGT $t'$ 
winning for the opponent.  This is why we can learn losing, but 
not winning, states from an AGT.

Reviewer B
~~~~~~~~~~

Thank you for your in-depth review!

(06) Experiments

We observe that Incremental Induction and Learning-Based backends 
of Demiurge individually can not solve the 12 instances; however 
they can solve them when combined in parallel with the 
template-based backend.  We conjecture that it is the 
template-based algorithm that solves these instances within the 
parallel portfolio.  This algorithm is very different from our 
method as well as other Demiurge algorithms.  We will validate 
this conjecture and more thoroughly evaluate our solver against 
the template-based method.

We will also add a theoretical and experimental comparison with 
the inductive synthesis method of [16].  Note that, as shown in 
[4], the algorithm of [16] is less efficient than Demiurge, which 
we compare against.

(07), (42) Strategy computation.

The method described in (42) is correct.  In addition, [9] 
describes a strategy extraction algorithm that operates on 
abstract game trees and does not require CPre computation.  This 
algorithm can be easily adapted to work with our method.

(08) Open sourcing

We are preparing an open source version of the tool for SYNTCOMP 
2016.

Reviewer C
~~~~~~~~~~

We will characterize the unique instances solved by our method.  
Intuitively, in these examples the winning set cannot be compactly 
represented using BDD or CNF and there exists a winning strategy, 
where at every round the player picks one of a small number of 
winning moves (i.e., there exists a compact winning abstract game 
tree for the player).

Regarding the number of unique solutions: while not a radical 
improvement, we push the virtual best in the sequential 
realizability track from 203 to 215 out of 250 instances.  As 
fewer unsolved instances remain, even such moderate improvements 
are hard to achieve.

It is also interesting that we are able to solve at least 12 
instances that are not solved by the winning solver in the 
competition, which is more than any other solver, thus emphasizing 
that our method has complementary strengthes to other techniques.

Reviewer D
~~~~~~~~~~

Indeed, BDD-based methods are still more scalable and versatile 
than SAT-based synthesis, including our method.  In this context, 
our contribution is two-fold.  First, we propose a SAT-based 
method that works on some classes of problems where BDDs blow up.  
Hence, it may be productive to combine this method with BDD or 
other SAT methods in a portfolio.  Second, by developing a new 
SAT-based synthesis technique, we contribute to the ongoing push 
to fully exploit the power of the SAT technology in synthesis, 
inspired by the success of SAT-based verification.

### 2016-04-22 paper.tex
Some of the example diagrams

\author{}
\institute{}

%\author{Alexander Legg\inst{1} 
%    \and Nina Narodytska\inst{2}
%    \and Leonid Ryzhyk\inst{2}}
%
%\institute{NICTA\thanks{NICTA is funded by the Australian Government as represented by the Department of Broadband,
%    Communications and the Digital Economy and the Australian Research Council through the ICT
%    Centre of Excellence program.} and UNSW \\
%    \email{alexander.legg@nicta.com.au}
%    \and Samsung Research America}

@@

@@

@@

                        node [left=4pt] {$\epsilon$}

@@

                    node [left=4pt] {$\beta$}

@@

                    node [left=4pt] {$\gamma$}
                node [right=4pt] {$\alpha$}

@@

>>>>

\author{Alexander Legg\inst{1} 
    \and Nina Narodytska\inst{2}
    \and Leonid Ryzhyk\inst{2}}

\institute{NICTA\thanks{NICTA is funded by the Australian Government as represented by the Department of Broadband,
    Communications and the Digital Economy and the Australian Research Council through the ICT
    Centre of Excellence program.} and UNSW \\
    \email{alexander.legg@nicta.com.au}
    \and Samsung Research America}

@@

                        edge from parent [fixed] node [left] {\texttt{req=0}}

@@

%%%                child {node [circle,draw] {}
%%%                    edge from parent [fixed] node [right] {\texttt{gr=1}}
%%%                }

@@

                        node [left=4pt] {\texttt{gr0=0, gr1=0}}
                        edge from parent [fixed] node [left] {\texttt{req=0}}

@@

                    node [left=4pt] {\texttt{gr0=0, gr1=0}}
                    edge from parent [fixed] node [left] {\texttt{req=0}}

@@

%%%                child {node [circle,draw] {}
%%%                    node [left=4pt] {\texttt{req=1}}
%%%                    edge from parent [fixed] node [right] {\texttt{gr=1}}
%%%                }
                node [left=4pt] {}

@@

                        edge from parent [fixed] node [right] {\texttt{req=1}}
